---
title: "FM Presentation 11th March"
author: "Centre for Policy Research"
date: "2023-03-10"
output: pdf_document
---

```{r setup, include=FALSE}
library(data.table)
library(readxl)
library(writexl)
library(dplyr)
library(MASS)
library(kableExtra)
library(foreign)
library(tidyverse)

AP_Household_Roster <- read_excel("Household Roster Youth Survey (7th Mar).xlsx")

AP_Household_Roster_Codebook <- read_excel("AP_Youth_Survey_Codebook.xlsx", sheet = 2)
colnames(AP_Household_Roster) <- c(AP_Household_Roster_Codebook$Variable_Name,"NAN")
attr(AP_Household_Roster, "variable.labels") <- AP_Household_Roster_Codebook$Column_Name


AP_Youth_Survey <- read_excel("youth_survey_responses (7th Mar).xlsx")
AP_Youth_Survey_Codebook <- read_excel("AP_Youth_Survey_Codebook.xlsx")
colnames(AP_Youth_Survey) <- c(AP_Youth_Survey_Codebook$Variable_Name, "NAN")
attr(AP_Youth_Survey, "variable.labels") <- AP_Youth_Survey_Codebook$Column_Name

##Plot theme
newtheme <- theme_bw() +
  theme(panel.border = element_rect(color = "darkgrey", size = 2), 
        panel.grid.major = element_blank(), legend.position = "bottom")

invlogit <- function(x){1/(1 + exp(-x))}

```

# Citywise Numbers


```{r, echo = F}
#Citywise Numbers
AP_Youth_Survey <- AP_Youth_Survey[AP_Youth_Survey$`City Name` != "N",]

City_Wise_Numbers <- as.data.frame(table(AP_Youth_Survey$`City Name`)); colnames(City_Wise_Numbers) <- c("City Name", "Responses")
City_Wise_Numbers

Small <- c("Kadiri", "Peddapuram", "Rayadurga", "Nidadavolu", "Kavali","Kondapalli") #Less than 1 Lakh
Medium <- c("Adoni", "Eluru", "Hindupur", "Kadapa", "Kakinada", "Narasaraopet", "Rajahmundry",
            "Tadipatri", "Tenali", "Tirupati") #1-4 Lakhs
Large <- c("Guntur", "Visakhapatnam", "Kurnool", "Nellore", "Vijayawada") #More than 4 Lakhs



AP_Youth_Survey$City_Size_Class <- ifelse(AP_Youth_Survey$`City Name`%in% Small, "Small",
                                          ifelse(AP_Youth_Survey$`City Name` %in% Medium, "Medium",
                                                 ifelse(AP_Youth_Survey$`City Name` %in% Large, "Large",
                                                        "NAN")))

Coastal_North <- c("Kakinada", "Peddapuram", "Rajahmundry", "Eluru", "Visakhapatnam", "Nidadavolu")
Coastal_South <- c("Guntur", "Narasaraopet", "Tenali", "Kavali", "Nellore", "Vijayawada", "Kondapalli")
Inland_South <- c("Hindupur", "Kadiri", "Rayadurga", "Tirupati","Adoni", "Kurnool", "Tadipatri", "Kadapa")


AP_Youth_Survey$City_Geo_Class <- ifelse(AP_Youth_Survey$`City Name`%in% Coastal_North, "Coastal_North",
                                          ifelse(AP_Youth_Survey$`City Name` %in% Coastal_South, "Coastal_South",
                                                 ifelse(AP_Youth_Survey$`City Name` %in% Inland_South, "Inland_South",
                                                        "NAN")))


```

# Crosstabs Replication

```{r}
#Satisfaction
#Past 5 years, AP doing better or worse?

as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_G_187)),1))[c(2,5,4,1,3),]

#Do you wish to move out of your town/city
as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_173)),1))[c(3,1,2),]

#What about out of Andhra, for those who want to move out
as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_176)),1))[c(3,1,2),]


#Satisfaction vs Movement
a <- as.data.frame((round(100*prop.table(table(AP_Youth_Survey$Y_G_187, AP_Youth_Survey$Y_F_173), 1),1))[c(2,5,4,1,3),c(3)]); colnames(a) <- c("Wanting To Leave (%)")
a

#Preference for cash schemes, more or less
as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_G_188)),1))[c(2,5,4,1,3),]


#Attribution for cash schemes
as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_E_80)),1))[c(1,4,5,6,3,7,2),]


#Satisfaction vs Cash Schemes
round(100*prop.table(table(AP_Youth_Survey$Y_G_187, AP_Youth_Survey$Y_G_188), 1),1)[c(2,5,4,1,3),c(2,5,4,1,3)]


#Satisfaction vs Attribution
round(100*prop.table(table(AP_Youth_Survey$Y_G_187, AP_Youth_Survey$Y_E_80), 1),1)[c(2,5,4,1,3),c(1,4,5,6,3,7,2)]
```

Labour Preference vs Skilling Enrollment

```{r, echo = F}
#Combining Skill Question Columns#### 
#In main survey
AP_Youth_Survey$YR_F_87 <- ifelse(AP_Youth_Survey$Y_F_81 == "Student", AP_Youth_Survey$Y_F_87,
                                  ifelse(AP_Youth_Survey$Y_F_81 == "Employed", AP_Youth_Survey$Y_F_123, AP_Youth_Survey$Y_F_160))

AP_Youth_Survey$YR_F_92 <- ifelse(AP_Youth_Survey$Y_F_81 == "Student", AP_Youth_Survey$Y_F_92,
                                  ifelse(AP_Youth_Survey$Y_F_81 == "Employed", AP_Youth_Survey$Y_F_128, AP_Youth_Survey$Y_F_165))

AP_Youth_Survey$YR_F_94 <- ifelse(AP_Youth_Survey$Y_F_81 == "Student", AP_Youth_Survey$Y_F_94,
                                  ifelse(AP_Youth_Survey$Y_F_81 == "Employed", AP_Youth_Survey$Y_F_130, AP_Youth_Survey$Y_F_167))


#Creating Variables
AP_Youth_Survey$IT_F87 <- grepl(c("Information Technology"), AP_Youth_Survey$YR_F_87, ignore.case = T) | grepl(c("Computer"), AP_Youth_Survey$YR_F_87, ignore.case = T)
AP_Youth_Survey$English_F87 <- grepl(c("English"), AP_Youth_Survey$YR_F_87, ignore.case = T) | grepl(c("Communication"), AP_Youth_Survey$YR_F_87, ignore.case = T)
AP_Youth_Survey$CompExam_F87 <- grepl(c("Competitive Exam"), AP_Youth_Survey$YR_F_87, ignore.case = T)
AP_Youth_Survey$SciEng_F87 <- grepl(c("Engineering"), AP_Youth_Survey$YR_F_87, ignore.case = T) | grepl(c("Science"), AP_Youth_Survey$YR_F_87, ignore.case = T)
AP_Youth_Survey$Repair_F87 <- grepl(c("Technical"), AP_Youth_Survey$YR_F_87, ignore.case = T) | grepl(c("Repair"), AP_Youth_Survey$YR_F_87, ignore.case = T)
AP_Youth_Survey$Craft_F87 <- grepl(c("Craftwork"), AP_Youth_Survey$YR_F_87, ignore.case = T)


#Interest
AP_Youth_Survey$IT_F92 <- grepl(c("Information Technology"), AP_Youth_Survey$YR_F_92, ignore.case = T) | grepl(c("Computer"), AP_Youth_Survey$YR_F_92, ignore.case = T)
AP_Youth_Survey$English_F92 <- grepl(c("English"), AP_Youth_Survey$YR_F_92, ignore.case = T) | grepl(c("Communication"), AP_Youth_Survey$YR_F_92, ignore.case = T)
AP_Youth_Survey$CompExam_F92 <- grepl(c("Competitive Exam"), AP_Youth_Survey$YR_F_92, ignore.case = T)
AP_Youth_Survey$SciEng_F92 <- grepl(c("Engineering"), AP_Youth_Survey$YR_F_92, ignore.case = T) | grepl(c("Science"), AP_Youth_Survey$YR_F_92, ignore.case = T)
AP_Youth_Survey$Repair_F92 <- grepl(c("Technical"), AP_Youth_Survey$YR_F_92, ignore.case = T) | grepl(c("Repair"), AP_Youth_Survey$YR_F_92, ignore.case = T)
AP_Youth_Survey$Craft_F92 <- grepl(c("Craftwork"), AP_Youth_Survey$YR_F_92, ignore.case = T)


AP_Youth_Survey$Total_Enr_F87 <- rowSums(AP_Youth_Survey[,c(217:222)+3])
AP_Youth_Survey$Total_Int_F92 <- rowSums(AP_Youth_Survey[,c(223:228)+3])


l1 <- as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_170, AP_Youth_Survey$IT_F87), 1),1))
l2 <- as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_170, AP_Youth_Survey$English_F87), 2),1))
l3 <- as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_170, AP_Youth_Survey$CompExam_F87), 2),1))
l4 <- as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_170, AP_Youth_Survey$SciEng_F87), 2),1))
l5 <- as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_170, AP_Youth_Survey$Repair_F87), 2),1))
l6 <- as.data.frame(round(100*prop.table(table(AP_Youth_Survey$Y_F_170, AP_Youth_Survey$Craft_F87), 2),1))


l1 <- l1[l1$Var2 == T,]; l2 <- l2[l2$Var2 == T,]; l3 <- l3[l3$Var2 == T,]; l4 <- l4[l4$Var2 == T,]; l5 <- l5[l5$Var2 == T,]; l6 <- l6[l6$Var2 == T,]

Labour_Skill <- cbind.data.frame(Labour_Pref = l1$Var1, l1$Freq, l2$Freq, l3$Freq, l4$Freq, l5$Freq, l6$Freq )
colnames(Labour_Skill) <- c("Labour Preference","IT", "English", "Competitive Exam", "Engineering/Science", "Technical/Repair", "Craftwork")

rm(l1,l2,l3,l4,l5,l6)
Labour_Skill
```

Skilling Enrollment vs Interest

```{r, echo = F}
#Skilling Enrollment vs Interest
c <- round(100*prop.table(table(AP_Youth_Survey$YR_F_87 != "No", AP_Youth_Survey$YR_F_92 != "No")),1)
rownames(c) <- c("Not Enrolled", "Enrolled"); colnames(c) <- c("No Intention", "Intention")
c
```


Enrollment/Intent vs Preference to Leave

```{r, echo = F}
#Row 1 - No Enrollment or Intent <- YR_F_87 == No & YR_F_92 == "No

d <- table(AP_Youth_Survey$YR_F_87 == "No" & AP_Youth_Survey$YR_F_92 == "No", AP_Youth_Survey$Y_F_173)
rownames(d) <- c("Enrolled/Intend to Enroll", "No Enrollment or Intent")
d
```


#Additions to be Made
Enrollment and intention 4 way table for all categories

```{r, echo = F}
#Enrollment and intention 4 way table for all categories
AP_Youth_Survey_Merged <- merge(AP_Youth_Survey, AP_Household_Roster[AP_Household_Roster$H_1 == "Self",], by.x = c("_uuid"), by.y = c("_submission__uuid"))
```


```{r, echo = T}
#Female
d <- round(100*prop.table(table(AP_Youth_Survey_Merged$YR_F_87[AP_Youth_Survey_Merged$Gender == "Female"] != "No", AP_Youth_Survey_Merged$YR_F_92[AP_Youth_Survey_Merged$Gender == "Female"] != "No")),1)
rownames(d) <- c("Not Enrolled", "Enrolled"); colnames(d) <- c("No Intention", "Intention")
d

#Male
d <- round(100*prop.table(table(AP_Youth_Survey_Merged$YR_F_87[AP_Youth_Survey_Merged$Gender == "Male"] != "No", AP_Youth_Survey_Merged$YR_F_92[AP_Youth_Survey_Merged$Gender == "Male"] != "No")),1)
rownames(d) <- c("Not Enrolled", "Enrolled"); colnames(d) <- c("No Intention", "Intention")
d

#Employed
d <- round(100*prop.table(table(AP_Youth_Survey_Merged$YR_F_87[AP_Youth_Survey_Merged$Y_F_81 == "Employed"] != "No", AP_Youth_Survey_Merged$YR_F_92[AP_Youth_Survey_Merged$Y_F_81 == "Employed"] != "No")),1)
rownames(d) <- c("Not Enrolled", "Enrolled"); colnames(d) <- c("No Intention", "Intention")
d

#Unemployed
d <- round(100*prop.table(table(AP_Youth_Survey_Merged$YR_F_87[AP_Youth_Survey_Merged$Y_F_81 == "Unemployed"] != "No", AP_Youth_Survey_Merged$YR_F_92[AP_Youth_Survey_Merged$Y_F_81 == "Unemployed"] != "No")),1)
rownames(d) <- c("Not Enrolled", "Enrolled"); colnames(d) <- c("No Intention", "Intention")
d

#Student
d <- round(100*prop.table(table(AP_Youth_Survey_Merged$YR_F_87[AP_Youth_Survey_Merged$Y_F_81 == "Student"] != "No", AP_Youth_Survey_Merged$YR_F_92[AP_Youth_Survey_Merged$Y_F_81 == "Student"] != "No")),1)
rownames(d) <- c("Not Enrolled", "Enrolled"); colnames(d) <- c("No Intention", "Intention")
d


#Female Student
d <- round(100*prop.table(table(AP_Youth_Survey_Merged$YR_F_87[AP_Youth_Survey_Merged$Y_F_81 == "Student" & AP_Youth_Survey_Merged$Gender == "Female"] != "No", AP_Youth_Survey_Merged$YR_F_92[AP_Youth_Survey_Merged$Y_F_81 == "Student" & AP_Youth_Survey_Merged$Gender == "Female"] != "No")),1)
rownames(d) <- c("Not Enrolled", "Enrolled"); colnames(d) <- c("No Intention", "Intention")
d


#Male Student
d <- round(100*prop.table(table(AP_Youth_Survey_Merged$YR_F_87[AP_Youth_Survey_Merged$Y_F_81 == "Student" & AP_Youth_Survey_Merged$Gender == "Male"] != "No", AP_Youth_Survey_Merged$YR_F_92[AP_Youth_Survey_Merged$Y_F_81 == "Student" & AP_Youth_Survey_Merged$Gender == "Male"] != "No")),1)
rownames(d) <- c("Not Enrolled", "Enrolled"); colnames(d) <- c("No Intention", "Intention")
d


```

Mobility by Marital Status and Gender

```{r}
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_F_176[AP_Youth_Survey_Merged$H_4 == "Currently Married"], AP_Youth_Survey_Merged$Gender[AP_Youth_Survey_Merged$H_4 == "Currently Married"]),2),1)
    
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_F_176[AP_Youth_Survey_Merged$H_4 != "Currently Married"], AP_Youth_Survey_Merged$Gender[AP_Youth_Survey_Merged$H_4 != "Currently Married"]),2),1)


round(100*prop.table(table(AP_Youth_Survey_Merged$Y_F_173[AP_Youth_Survey_Merged$H_4 == "Currently Married"], AP_Youth_Survey_Merged$Gender[AP_Youth_Survey_Merged$H_4 == "Currently Married"]),2),1)
    
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_F_173[AP_Youth_Survey_Merged$H_4 != "Currently Married"], AP_Youth_Survey_Merged$Gender[AP_Youth_Survey_Merged$H_4 != "Currently Married"]),2),1)
             


```

Satisfaction Responses Disaggregated Demographically

```{r}
#Gender
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_G_187, AP_Youth_Survey_Merged$Gender), 2),1)[c(2,5,4,1,3),]

#Marital Status
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_G_187, AP_Youth_Survey_Merged$H_4 == "Currently Married"), 2),1)[c(2,5,4,1,3),]

#Age 
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_G_187, AP_Youth_Survey_Merged$Age >= 25), 2),1)[c(2,5,4,1,3),]

#Education
College <- c("Diploma/Certificate Course", "Graduate: Technical", "Graduate: General", "Postgraduate and above")

round(100*prop.table(table(AP_Youth_Survey_Merged$Y_G_187, (AP_Youth_Survey_Merged$H_5 %in% College) == T), 2),1)[c(2,5,4,1,3),]

#City Size Class
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_G_187, AP_Youth_Survey_Merged$City_Size_Class), 2),1)[c(2,5,4,1,3),]


#City Geo Region
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_G_187, AP_Youth_Survey_Merged$City_Geo_Class), 2),1)[c(2,5,4,1,3),]

#Caste Category
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_G_187, AP_Youth_Survey_Merged$Y_A_15), 2),1)[c(2,5,4,1,3), c(1,3,5,6,4,2)]

```


Attribution Responses Disaggregated Demographically

```{r}
#Gender
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_E_80, AP_Youth_Survey_Merged$Gender), 2),1)[c(1,4,5,6,3,7,2),]

#Marital Status
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_E_80, AP_Youth_Survey_Merged$H_4 == "Currently Married"), 2),1)[c(1,4,5,6,3,7,2),]

#Age 
round(100*prop.table(table(AP_Youth_Survey_Merged$Y_E_80, AP_Youth_Survey_Merged$Age >= 25), 2),1)[c(1,4,5,6,3,7,2),]

#Education
College <- c("Diploma/Certificate Course", "Graduate: Technical", "Graduate: General", "Postgraduate and above")

round(100*prop.table(table(AP_Youth_Survey_Merged$Y_E_80, (AP_Youth_Survey_Merged$H_5 %in% College) == T), 2),1)[c(1,4,5,6,3,7,2),]


#City Size Class
round(100*prop.table(table(AP_Youth_Survey$Y_E_80, AP_Youth_Survey$City_Size_Class), 2),1)[c(1,4,5,6,3,7,2),]

#City Geo Region
round(100*prop.table(table(AP_Youth_Survey$Y_E_80, AP_Youth_Survey$City_Geo_Class), 2),1)[c(1,4,5,6,3,7,2),]


#Caste Category
round(100*prop.table(table(AP_Youth_Survey$Y_E_80, AP_Youth_Survey$Y_A_15), 2),1)[c(1,4,5,6,3,7,2),c(1,3,5,6,4,2)]

```


# Presentation Pertaining to Social Schemes and Citizen Support

I. Support for Education
```{r}
A <- AP_Youth_Survey

ammavodi <- A[grep("Ammavodi", A$Y_E_55), ]
jvd <- A[grep("Jagananna Vidya Deevena", A$Y_E_55), ]
jvvd <- A[grep("Jagananna VasathI Deevena", A$Y_E_55), ]
jvk <- A[grep("Jagananna Vidya Kanuka", A$Y_E_55), ]
rte <- A[grep("Right to Education", A$Y_E_55), ]
pms <- A[grep("Pre-Matric Scholarship", A$Y_E_55), ]
fls <- A[grep("Free Laptop Scheme", A$Y_E_55), ]
other <- A[grep("Other", A$Y_E_55), ]

beneficiaries <- c(nrow(ammavodi), nrow(jvd), nrow(jvvd), nrow(jvk), nrow(rte), nrow(pms), nrow(fls), nrow(other))
Scheme <- c("Ammavodi", "Jagananna Vidya Deevena", "Jagananna Vasathi Deevena", "Jagananna Vidya Kanuka", "Right to Education", "Pre-Matric Scholarship", "Free Laptop Scheme", "Others")

edbenefits_dta <- data.frame (Scheme, beneficiaries) %>%
mutate (Proportions = round(beneficiaries*100/sum(beneficiaries),1))

edbenefits_dta$Scheme <- as.factor(edbenefits_dta$Scheme)
edbenefits_dta$Scheme <- factor(edbenefits_dta$Scheme, levels = c("Ammavodi", "Jagananna Vidya Deevena", "Jagananna Vasathi Deevena", "Jagananna Vidya Kanuka", "Right to Education", "Others", "Free Laptop Scheme", "Pre-Matric Scholarship"))


edbenefits_plot <- ggplot(edbenefits_dta, aes(x= Scheme, y= Proportions, fill = Scheme)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text (aes(label = Proportions), position = position_dodge(0.1), vjust = -1) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = function(`Scheme`) str_wrap(`Scheme`, width = 10)) +
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percentage", subtitle = "Support for Education") + newtheme

edbenefits_plot
```

II. Support for Health
```{r}
arogyasri <- A[grep("Arogyasri", A$Y_E_60), ]
pmjay <- A[grep("Pradhan Mantri Jan Aarogya Yojana", A$Y_E_60), ]
fh <- A[grep("Free Hospitalization", A$Y_E_60), ]
jsy <- A[grep("Janani Suraksha Yojana", A$Y_E_60), ]
pmmvy <- A[grep("Pradhan Mantri Matru Vandana Yojana", A$Y_E_60), ]
other <- A[grep("Other", A$Y_E_60), ]

beneficiaries <- c(nrow(arogyasri), nrow(pmjay), nrow(fh), nrow(jsy), nrow(pmmvy), nrow(other))
Scheme <- c("Arogyasri", "Pradhan Mantri Jan Aarogya Yojana (PMJAY)", "Free Hospitalization", "Janani Suraksha Yojana", "Pradhan Mantri Matru Vandana Yojana (PMMVY)", "Others")

healthbenefits_dta <- data.frame (Scheme, beneficiaries) %>%
mutate (Proportions = round(beneficiaries*100/sum(beneficiaries),1))

healthbenefits_dta$Scheme <- factor(healthbenefits_dta$Scheme, levels = c("Arogyasri", "Free Hospitalization", "Pradhan Mantri Jan Aarogya Yojana (PMJAY)", "Janani Suraksha Yojana", "Pradhan Mantri Matru Vandana Yojana (PMMVY)", "Others"))


healthbenefits_plot <- ggplot(healthbenefits_dta, aes(x= Scheme, y= Proportions, fill = Scheme)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text (aes(label = Proportions), position = position_dodge(0.1), vjust = -1) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = function(`Scheme`) str_wrap(`Scheme`, width = 10)) +
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percentage", subtitle = "Support for Health") + newtheme

healthbenefits_plot
```

III. Support for Housing
```{r}
illu <- A[grep("Pedalandariki Illu", A$Y_E_50), ]
pmay <- A[grep("Pradhan Mantri Awaas Yojana", A$Y_E_50), ]
ray <- A[grep("RAY", A$Y_E_50), ]
other <- A[grep("Other", A$Y_E_50), ]

beneficiaries <- c(nrow(illu), nrow(pmay), nrow(ray), nrow(other))
Scheme <- c("Pedalandariki Illu", "Pradhan Mantri Awaas Yojana", "RAY (Rajeev Awas Yojana)", "Others")

housingbenefits_dta <- data.frame (Scheme, beneficiaries) %>%
mutate (Proportions = round(beneficiaries*100/sum(beneficiaries),1))

housingbenefits_dta$Scheme <- factor(housingbenefits_dta$Scheme, levels = c("Pedalandariki Illu", "Pradhan Mantri Awaas Yojana", "RAY (Rajeev Awas Yojana)", "Others"))

housingbenefits_plot <- ggplot(housingbenefits_dta, aes(x= Scheme, y= Proportions, fill = Scheme)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text (aes(label = Proportions), position = position_dodge(0.1), vjust = -1) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = function(`Scheme`) str_wrap(`Scheme`, width = 10)) +
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percentage", subtitle = "Support for Housing") + newtheme

housingbenefits_plot

```
IV. Cash Support (DBT)
```{r}
pensions <- A[grep("Pension", A$Y_E_65), ]
pmkisan <- A[grep("PM Kisan", A$Y_E_65), ]
cheyutha <- A[grep("YSR Cheyutha", A$Y_E_65), ]
kapuneshtam <- A[grep("YSR Kapu Neshtam", A$Y_E_65), ]
ebcneshtam <- A[grep("YSR EBC Neshtam", A$Y_E_65), ]
Others <- A[grep("Other", A$Y_E_65), ]
rythubharosa <- A[grep("Rythu Bharosa", A$Y_E_65), ]

beneficiaries <- c(nrow(pensions), nrow(pmkisan), nrow(cheyutha), nrow(kapuneshtam), nrow(ebcneshtam), nrow(Others), nrow(rythubharosa))
Scheme <- c("Pension", "PM Kisan", "YSR Cheyutha", "YSR Kapu Neshtam", "YSR EBC Neshtam", "Others", "Rythu Bharosa")

cashbenefits_dta <- data.frame (Scheme, beneficiaries) %>%
mutate (Proportions = round(beneficiaries*100/sum(beneficiaries),1))

cashbenefits_dta$Scheme <- factor(cashbenefits_dta$Scheme, levels = c("Pension", "YSR Cheyutha", "Rythu Bharosa", "YSR Kapu Neshtam", "PM Kisan", "YSR EBC Neshtam", "Others"))

cashbenefits_plot <- ggplot(cashbenefits_dta, aes(x= Scheme, y= Proportions, fill = Scheme)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text (aes(label = Proportions), position = position_dodge(0.1), vjust = -1) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = function(`Scheme`) str_wrap(`Scheme`, width = 10)) +
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percentage", subtitle = "Cash Support") + newtheme

cashbenefits_plot

```

V. Business Support, Loan Support & Loan Forgiveness
```{r}
mudra <- A[grep("MUDRA", A$Y_E_70), ]
aasara <- A[grep("YSR Aasara", A$Y_E_70), ]
adarsham <- A[grep("YSR Adarsham", A$Y_E_70), ]
sunnavaddi <- A[grep("YSR Sunna Vaddi", A$Y_E_70), ]
Others <- A[grep("Other", A$Y_E_70), ]

beneficiaries <- c(nrow(mudra), nrow(aasara),nrow(adarsham), nrow(sunnavaddi), nrow(Others))
Scheme <- c("MUDRA", "YSR Aasara", "YSR Adarsham", "YSR Sunna Vaddi", "Others")

loanbenefits_dta <- data.frame (Scheme, beneficiaries) %>%
mutate (Proportions = round(beneficiaries*100/sum(beneficiaries),1))

loanbenefits_dta$Scheme <- factor(loanbenefits_dta$Scheme, levels = c("YSR Sunna Vaddi", "YSR Aasara", "Others", "MUDRA", "YSR Adarsham"))

loanbenefits_plot <- ggplot(loanbenefits_dta, aes(x= Scheme, y= Proportions, fill = Scheme)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text (aes(label = Proportions), position = position_dodge(0.1), vjust = -1) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = function(`Scheme`) str_wrap(`Scheme`, width = 10)) +
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percentage", subtitle = "Business Support, Loan Support & Loan Forgiveness") + newtheme

loanbenefits_plot

```
VI. Support for Household Services & Infrastructure

```{r}
sanitation <- A[grep("Sanitation", A$Y_E_75), ]
watersupply <- A[grep("Water supply", A$Y_E_75), ]
lpg <- A[grep("LPG", A$Y_E_75), ]
childcare <- A[grep("To take care of children", A$Y_E_75), ]
disability <- A[grep("disability", A$Y_E_75), ]
pension <- A[grep("Pension", A$Y_E_75), ]

beneficiaries <- c(nrow(sanitation), nrow(watersupply), nrow(lpg), nrow(childcare), nrow(disability), nrow(pension))
Scheme <- c("Sanitation", "Water supply", "LPG", "To take care of children", "To take care of person(s) with disability", "Pensions")

services_dta <- data.frame (Scheme, beneficiaries) %>%
mutate (Proportions = round(beneficiaries*100/sum(beneficiaries),1))

services_dta$Scheme <- factor(services_dta$Scheme, levels = c("Water supply", "Sanitation", "LPG", "Pensions" , "To take care of children", "To take care of person(s) with disability"))

services_plot <- ggplot(services_dta, aes(x= Scheme, y= Proportions, fill = Scheme)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text (aes(label = Proportions), position = position_dodge(0.1), vjust = -1) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = function(`Scheme`) str_wrap(`Scheme`, width = 10)) +
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percentage", subtitle = "Support for Household Services & Infrastructure") + newtheme

services_plot
```

VII. Attribution Questions
```{r}
Y_E_80 <- as.data.frame(table(AP_Youth_Survey$Y_E_80)) %>% 
mutate (Proportions = round(Freq*100/sum(Freq),1)) %>% 
rename ("Response" = Var1) %>% 
rename ("Count" = Freq) 

Y_E_80$Response <- as.factor(Y_E_80$Response)

Y_E_80$Response <- factor(Y_E_80$Response, levels = c("Chief Minister", "Government Officials", "Don't know", "Ward Councillor", "MLA", "Prime Minister", "MP"))

Y_E_80_plot <- ggplot(Y_E_80, aes(x= Response, y= Proportions, fill = Response)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text (aes(label = Proportions), position = position_dodge(0.1), vjust = -1) +
  scale_y_continuous(limits = c(0,80)) +
  scale_x_discrete(labels = function(`Response`) str_wrap(`Response`, width = 10)) +
  #scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percentage", subtitle = "Attribution of Credit (by position)") + newtheme

Y_E_80_plot
```
VIII. Visualizing respondents not covered by schemes
```{r}
No_housing <- A[grep("No", A$Y_E_50), ]
No_education <- A[grep("No", A$Y_E_55), ]
No_health <- A[grep("No", A$Y_E_60), ]
No_cashsupport <- A[grep("No", A$Y_E_65), ]
No_loan <- A[grep("No", A$Y_E_70), ]
No_services <- A[grep("No", A$Y_E_75), ]

no_responses <- c(nrow(No_housing), nrow(No_education), nrow(No_health), nrow(No_cashsupport), nrow(No_loan), nrow(No_services))
Benefits <- c("Housing", "Education", "Health", "Cash Support", "Debt Support, Business Support & Loan Forgiveness", "Household Services and Infrastructure")

not_recieved <- data.frame(Benefits, no_responses)


not_recieved <- not_recieved %>% 
mutate ("Proportions (Not Recieved)" = round(no_responses*100/sum(no_responses),1)) %>% 
dplyr::select(-no_responses)

unknown_housing <- A[grep("Don't Know", A$Y_E_50), ]
unknown_education <- A[grep("Don't know", A$Y_E_55), ]
unknown_health <- A[grep("Don't know", A$Y_E_60), ]
unknown_cashsupport <- A[grep("Don't Know", A$Y_E_65), ]
unknown_loan <- A[grep("Don't Know", A$Y_E_70), ]
unknown_services <- A[grep("Don't Know", A$Y_E_75), ]

no_responses <- c(nrow(unknown_housing), nrow(unknown_education), nrow(unknown_health), nrow(unknown_cashsupport), nrow(unknown_loan), nrow(unknown_services))
Benefitss <- c("Housing", "Education", "Health", "Cash Support", "Debt Support, Business Support & Loan Forgiveness", "Household Services and Infrastructure")
group <- c("Didn't know", "Didn't know", "Didn't know", "Didn't know", "Didn't know", "Didn't know")

unknown <- data.frame(Benefitss, no_responses)

unknown <- unknown %>% 
mutate ("Proportions (Didn't know)" = round(no_responses*100/sum(no_responses),1)) %>% 
dplyr::select(-no_responses)

unknown_noresponse <- cbind(not_recieved, unknown) %>% 
dplyr::select (-Benefitss)

unknown_noresponse %>% 
kbl(caption = "Support to Citizens: Not Recieved or Didn't know ", align = "l")%>%
  kable_classic(full_width = F, html_font = "Cambria", font_size = 15)
```

```{r}
##Organizing Outcome Variables

#Support for Housing
y1 <- ifelse(AP_Youth_Survey_Merged$Y_E_50 == "No", 0, 1)

#Support for Education
y2 <- ifelse(AP_Youth_Survey_Merged$Y_E_55 == "No", 0, 1)

#Support for Health
y3 <- ifelse(AP_Youth_Survey_Merged$Y_E_60 == "No", 0, 1)

#Cash Support
y4 <- ifelse(AP_Youth_Survey_Merged$Y_E_65 == "No", 0, 1)

#Business Support & Debt Support
y5 <- ifelse(AP_Youth_Survey_Merged$Y_E_70 == "No", 0, 1)

#Household Services & Infrastructure
y6 <- ifelse(AP_Youth_Survey_Merged$Y_E_75 == "No", 0, 1)

##Organising Predictors
age <- AP_Youth_Survey_Merged$Age

male <- ifelse(AP_Youth_Survey_Merged$Gender == "Male", 1, 0)
female <- ifelse(AP_Youth_Survey_Merged$Gender == "Female", 1, 0)

rel_hindu <- ifelse(AP_Youth_Survey_Merged$Y_A_13 == "Hinduism", 1, 0)
rel_muslim <- ifelse(AP_Youth_Survey_Merged$Y_A_13 == "Islam", 1, 0)
rel_christ <- ifelse(AP_Youth_Survey_Merged$Y_A_13 == "Christianity", 1, 0)
rel_others <- ifelse((AP_Youth_Survey_Merged$Y_A_13 %in% c("Christianity", "Hinduism", "Islam")) == F, 1, 0)


caste_gen <- ifelse(AP_Youth_Survey_Merged$Y_A_15 == "General (OC)", 1, 0)
caste_sc <- ifelse(AP_Youth_Survey_Merged$Y_A_15 == "Scheduled Caste (SC)", 1, 0)
caste_st <- ifelse(AP_Youth_Survey_Merged$Y_A_15 == "Scheduled Tribe (ST)", 1, 0)
caste_bc <- ifelse(AP_Youth_Survey_Merged$Y_A_15 == "Backward Caste (BC)", 1, 0)
caste_others <- ifelse((AP_Youth_Survey_Merged$Y_A_15 %in% c("Backward Caste (BC)", "Scheduled Tribe (ST)", "Scheduled Caste (SC)", "General (OC)")) == F, 1, 0)

prim_act <- AP_Youth_Survey_Merged$Y_F_81

city_size <- AP_Youth_Survey_Merged$City_Size_Class
```


```{r}
#Housing: Running the model and getting a probability estimate 
logit.fit.1 <- glm(y1 ~ age + female + factor(prim_act) + factor(city_size) + rel_others + rel_muslim + rel_christ + caste_others + caste_sc + caste_st + caste_bc, family=binomial(link = "logit")) 
summary(logit.fit.1)

logit.fit.1$coefficients

x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)  ## OC, Hindu, Employed, Big City, Male

invlogit(logit.fit.1$coefficients %*% x)


#Simulations to generate predicted values
x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)

set.seed(1234)
sim.coef <- mvrnorm(15000, logit.fit.1$coefficients, vcov(logit.fit.1))

predvals.sim.0 <- invlogit(sim.coef %*% x)

quantile(predvals.sim.0, seq(0,1,0.01))
```

```{r}
#Education: Running the model and getting a probability estimate 
logit.fit.2 <- glm(y2 ~ age + female + factor(prim_act) + factor(city_size) + rel_others + rel_muslim + rel_christ + caste_others + caste_sc + caste_st + caste_bc, family=binomial(link = "logit")) 


logit.fit.2$coefficients

x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)  ## OC, Hindu, Employed, Big City, Male

invlogit(logit.fit.2$coefficients %*% x)


#Simulations to generate predicted values
x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)

set.seed(1234)
sim.coef <- mvrnorm(15000, logit.fit.2$coefficients, vcov(logit.fit.2))

predvals.sim.0 <- invlogit(sim.coef %*% x)

quantile(predvals.sim.0, seq(0,1,0.01))
```

```{r}
#Health: Running the model and getting a probability estimate 
logit.fit.3 <- glm(y3 ~ age + female + factor(prim_act) + factor(city_size) + rel_others + rel_muslim + rel_christ + caste_others + caste_sc + caste_st + caste_bc, family=binomial(link = "logit")) 
summary(logit.fit.3)

logit.fit.3$coefficients

x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)  ## OC, Hindu, Employed, Big City, Male

invlogit(logit.fit.3$coefficients %*% x)


#Simulations to generate predicted values
x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)

set.seed(1234)
sim.coef <- mvrnorm(15000, logit.fit.3$coefficients, vcov(logit.fit.3))

predvals.sim.0 <- invlogit(sim.coef %*% x)

quantile(predvals.sim.0, seq(0,1,0.01))
```

```{r}
#Cash Support: Running the model and getting a probability estimate 
logit.fit.4 <- glm(y4 ~ age + female + factor(prim_act) + factor(city_size) + rel_others + rel_muslim + rel_christ + caste_others + caste_sc + caste_st + caste_bc, family=binomial(link = "logit")) 
summary(logit.fit.4)

logit.fit.4$coefficients

x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)  ## OC, Hindu, Employed, Big City, Male

invlogit(logit.fit.4$coefficients %*% x)


#Simulations to generate predicted values
x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)

set.seed(1234)
sim.coef <- mvrnorm(15000, logit.fit.4$coefficients, vcov(logit.fit.4))

predvals.sim.0 <- invlogit(sim.coef %*% x)

quantile(predvals.sim.0, seq(0,1,0.01))
```

```{r}
#Business Support: Running the model and getting a probability estimate 
logit.fit.5 <- glm(y5 ~ age + female + factor(prim_act) + factor(city_size) + rel_others + rel_muslim + rel_christ + caste_others + caste_sc + caste_st + caste_bc, family=binomial(link = "logit")) 
summary(logit.fit.5)

logit.fit.5$coefficients

x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)  ## OC, Hindu, Employed, Big City, Male

invlogit(logit.fit.5$coefficients %*% x)


#Simulations to generate predicted values
x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)

set.seed(1234)
sim.coef <- mvrnorm(15000, logit.fit.5$coefficients, vcov(logit.fit.5))

predvals.sim.0 <- invlogit(sim.coef %*% x)

quantile(predvals.sim.0, seq(0,1,0.01))
```

```{r}
#Household Services & Infrastructure: Running the model and getting a probability estimate 
logit.fit.6 <- glm(y6 ~ age + female + factor(prim_act) + factor(city_size) + rel_others + rel_muslim + rel_christ + caste_others + caste_sc + caste_st + caste_bc, family=binomial(link = "logit")) 
summary(logit.fit.6)

logit.fit.6$coefficients

x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)  ## OC, Hindu, Employed, Big City, Male

invlogit(logit.fit.6$coefficients %*% x)


#Simulations to generate predicted values
x <- c(1,25, 0, 0, 0, 0,0, 0,0,0,0,0,0,0)

set.seed(1234)
sim.coef <- mvrnorm(15000, logit.fit.6$coefficients, vcov(logit.fit.6))

predvals.sim.0 <- invlogit(sim.coef %*% x)

quantile(predvals.sim.0, seq(0,1,0.01))
```


Plot: Support to citizens across selected sectors (Housing, Education, Health, Cash Support, Business/Loan Support)

```{r, fig.width = 10}
Neg_Resp <- c("No", "Don't Know", "Don't know")

vec <- c(62, 67, 72, 77, 82) + 1

c <- cbind.data.frame(Col_No = as.numeric(vec), Var_Codes = colnames(AP_Youth_Survey_Merged)[vec], Q_Name = AP_Youth_Survey_Codebook$Column_Name[vec - 1])

Yes_Resp <- Tot_Resp <- rep(NA, length(vec))

for (i in 1:nrow(c)) {
  
  t <- as.data.frame(table(AP_Youth_Survey_Merged[,c$Col_No[i]] %in% Neg_Resp))
  Yes_Resp[i] <- t$Freq[t$Var1 == F]
  Tot_Resp[i] <- sum(t$Freq, na.rm = T)
  
  
}

c <- cbind.data.frame(c, Yes_Resp, Tot_Resp)
c$Benefit_Rate = round(100*c$Yes_Resp/c$Tot_Resp, 2)

names <- c("Housing", "Education", "Health", "Cash Support", "Business Support/Loan")

bp <- barplot(c$Benefit_Rate, names.arg = names, ylim = c(0,55), border = NA, col = "dodgerblue", main = "Proportion of Respondents Covered by Schemes", xlab = "Scheme", ylab = "Percentage of Respondents")
text(bp, c$Benefit_Rate, round(c$Benefit_Rate, 1), pos = 3)
```

## Cross tabulation: Schemes vs Preference of Schemes

```{r}
#Housing
round(prop.table(table((AP_Youth_Survey$Y_E_50 %in% Neg_Resp) == F, AP_Youth_Survey$Y_G_188), 1)*100, 2)

#Health
round(prop.table(table((AP_Youth_Survey$Y_E_55 %in% Neg_Resp) == F, AP_Youth_Survey$Y_G_188), 1)*100, 2)

#Education
round(prop.table(table((AP_Youth_Survey$Y_E_60 %in% Neg_Resp) == F, AP_Youth_Survey$Y_G_188), 1)*100, 2)

#Cash Support
round(prop.table(table((AP_Youth_Survey$Y_E_65 %in% Neg_Resp) == F, AP_Youth_Survey$Y_G_188), 1)*100, 2)

#Business Support
round(prop.table(table((AP_Youth_Survey$Y_E_70 %in% Neg_Resp) == F, AP_Youth_Survey$Y_G_188), 1)*100, 2)
```

## Cross tabulation: Schemes vs Attribution


```{r}
#Housing
round(prop.table(table((AP_Youth_Survey$Y_E_50 %in% Neg_Resp) == F, AP_Youth_Survey$Y_E_80), 1)*100, 2)

#Health
round(prop.table(table((AP_Youth_Survey$Y_E_55 %in% Neg_Resp) == F, AP_Youth_Survey$Y_E_80), 1)*100, 2)

#Education
round(prop.table(table((AP_Youth_Survey$Y_E_60 %in% Neg_Resp) == F, AP_Youth_Survey$Y_E_80), 1)*100, 2)

#Cash Support
round(prop.table(table((AP_Youth_Survey$Y_E_65 %in% Neg_Resp) == F, AP_Youth_Survey$Y_E_80), 1)*100, 2)

#Business Support
round(prop.table(table((AP_Youth_Survey$Y_E_70 %in% Neg_Resp) == F, AP_Youth_Survey$Y_E_80), 1)*100, 2)
```
